\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Journal 4}
\author{uchinta }
\date{September 2018}

\begin{document}

\maketitle

\section{Progress}
To start off with, the process of writing this study was really confusing. IO had so many questions to myself on what survey I need to do and what will be a useful for my future plan. So I started reading several papers and also the survey paper that was shared in the git hub. Somehow after a lot of struggle back and forth I had an idea on working on something that will be a part of my dissertation.

The topic I selected is something that is not what I am working currently but the topic is what I want to branch out from my projects right now. The topic is facial expression analysis. I know that is a broad topic and there is only one expression I need to care about which is "Confusion". Then I started reading papers on facial expression analysis. The mistake I have done here took a lot of my time. I kept reading the papers thoroughly to understand what the authors are saying. Eventually I realized we need to browse and skim the papers. Then I started doing that, but there are so many surveys already done on facial expression techniques. I was really confused of what I am supposed to do. After the class on Monday I got a clear idea of what I want to do. Now I need to search for more papers that deal with facial expression analysis techniques using the video streaming. Hopefully I will be successful in finishing my draft in time.   

\end{document}
